Physical Chemistry Tips

### 2015-12-08 physical_chemistry/latex/pchem_tips.tex
blah

\begin{align*}
  \mbox{Clapeyron Equation}\\
  \frac{dP}{dT} &= \frac{\Delta S}{\Delta V} = \frac{\Delta H}{T\Delta V}\\
  a_i &= \frac{P_i}{P_i*}\hspace{2cm}\mbox{The activity is the vapor pressure over the pure vapor pressure}\\
  P_i &= x_iP_i*\hspace{2cm}\mbox{xi is mol frawction of i in liquid}\\
  a_i &= x_i\hspace{2cm}\mbox{Ideal solutions only}\\
  \mu_i(l) &= \mu_i(l)\degree + RT\ln(x_i)\hspace{2cm}\mbox{Ideal solutions only}\\
  P_i &= y_iP = K_ix_i\hspace{2cm}\mbox{Henry's law}\\
\end{align*}

>>>>

\begin{align*}
  \mbox{Clapeyron Equation}\\
  \frac{dP}{dT} &= \frac{\Delta S}{\Delta V} = \frac{\Delta H}{T\Delta V}\\
  a_i &= \frac{P_i}{P_i*}\hspace{2cm}\mbox{The activity is the vapor pressure over the pure vapor pressure}\\
  \frac{dP}{dT} &= \frac{P\Delta_{vap}H}{RT^2}\hspace{2cm}\mbox{Clausius-Clapeyron}\\
  \ln\left(\frac{P_2}{P_1}\right) &= \frac{\Delta_{vap}H(T_2-T_1)}{RT_1T_2}\\
  P_i &= x_iP_i*\hspace{2cm}\mbox{xi is mol frawction of i in liquid}\\
  a_i &= x_i\hspace{2cm}\mbox{Ideal solutions only}\\
  \mu_i(l) &= \mu_i(l)\degree + RT\ln(x_i)\hspace{2cm}\mbox{Ideal solutions only}\\
  P_i &= y_iP = K_ix_i\hspace{2cm}\mbox{Henry's law}\\
\end{align*}

\begin{align*}
  \Delta T_f &= \frac{RT^2_{fus,A}M_am_B}{\Delta_{fus}H_A\degree} = K_fm_B\\
\end{align*}

\begin{align*}
  \Delta_{sub} H &= \Delta_{vap} H + \Delta_{fus} H\\
\end{align*}
